---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pathformatr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![R build status](https://github.com/mcguinlu/pathformatr/workflows/R-CMD-check/badge.svg)](https://github.com/mcguinlu/pathformatr/actions)
<!-- badges: end -->

The purpose of `pathformatr` is singular and simple - to allow you to use the RStudio file path auto-complete functionality and then quickly reformat your file path to use comma seperated elements:

``` {r, eval = FALSE}
here::here("data/2020/06/01/data.csv")
# or
here::here("data\2020\06\01\data.csv")

# becomes

here::here("data","2020","06","01","data.csv")
```

This functionality is available via the `here_clean_path()` function, but is designed to work best via an RStudio addin - simply highlight your file path, browse to the `pathformatr` section in the RStudio Addins drop-down menu, and select "Format path for use with here::here()".

Alternatively you can [bind the functionality to a keyboard shortcut](https://support.rstudio.com/hc/en-us/articles/206382178-Customizing-Keyboard-Shortcuts) (I personally like mapping it to `CRTL+/`).

### `here_clean_all()`

A second helper function reformats. By default, it targets `here()` and `file.path()` calls, though users can specify that only one of these should be targetted, or add additional targets, using the `fns` argument.


## Motivation

My motivation for this project was primarily to have a reason to play around with the RStudio interface (via the `rstudioapi` package) and to get to grips with `regex` syntax.

## To Do

* Make a video demonstrating the functionality.
